Effects of Reynolds Number on the Performance and Near-Wake of a Cross-Flow Turbine

### 2014-06-16 paper.tex
Make titles regular title case
Add some info to test plan, including table of Reynolds numbers

% Full title of the paper (Capitalized)
\Title{Effects of Reynolds number on the performance and near-wake of a
cross-flow turbine}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ Center for Ocean Renewable Energy, 
University of New Hampshire, 24 Colovos Rd., Durham, NH, USA}

@@

% Abstract (Do not use inserted blank lines, i.e. \\) 
\abstract{
This is the abstract section. The abstract should be one section and count less than 200 words.
}

@@

\section{Experimental Section}

Experiments were performed in the University of New Hampshire's tow/wave tank
turbine test bed. The turbine model is dubbed the UNH-RVAT, for Reference
Vertical Axis Turbine, which is designed to be a generic case for numerical
model testing, similar to the Sandia National Labs/US Department of Energy RM2
River Turbine. Details of the turbine are described in \cite{Bachant2014_JOT}.

@@

\subsection{Test plan}

Approximately 1500 tows were performed, each one used for
a single data point on either a performance curve or wake map.

A performance curve

\subsection{Data processing}

@@

\subsection{Performance curves}

@@

\subsection{Wake characteristics}

>>>>

% Full title of the paper (Capitalized)
\Title{Effects of Reynolds Number on the Performance and Near-Wake of a
Cross-Flow Turbine}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one
% affiliation.)
\address{%
$^{1}$ Center for Ocean Renewable Energy, University of New Hampshire, 24
Colovos Rd., Durham, NH, USA}

@@

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{This is the abstract section. The abstract should be one section and
count less than 200 words. }

@@

\section{Experimental Setup}

Experiments were performed in the University of New Hampshire's tow/wave tank
turbine test bed. The turbine model is dubbed the UNH-RVAT, for Reference
Vertical Axis Turbine, which is designed to be a generic case for numerical
model testing, similar to the Sandia National Labs/US Department of Energy RM2
River Turbine. Details of the turbine and experimental setup are described in
\cite{Bachant2014_JOT}.

@@

\subsection{Test Plan}

Approximately 1500 tows were performed, each one used for a single data point on
either a performance curve or wake map. A performance curve consisted of 31
tows, where during each tow the mean turbine tip speed ratio was held constant,
ranging from 0.1--3.1 in 0.1 increments. Full performance curve data were
acquired for tow speeds from 0.4 to 1.2 m/s in 0.2 m/s increments, for which
turbine diameter and approximate blade chord Reynolds number are presented in
Table~\ref{tab:Re}. Performance was also measured for $\lambda=1.9$ at tow
speeds [0.3, 0.5, 0.7, 0.9, 1.1, 1.3] m/s, each of which consisted of two tows.

\begin{table}
\centering
\begin{tabular}{ccc}
Tow speed (m/s) & $Re_D$ & $Re_c$ ($\lambda = 1.9$) \\ 
\hline
0.2 & $2.0 \times 10^5$ &  \\ 
0.4 & $4.0 \times 10^5$ &  \\ 
0.6 & $6.0 \times 10^5$ &  \\ 
0.8 & $8.0 \times 10^5$ &  \\ 
1.0 & $1.0 \times 10^6$ &  \\ 
1.2 & $1.2 \times 10^6$ &  \\ 
\end{tabular} 
\caption{Turbine diameter and approximate blade chord Reynolds numbers for the
tow speeds at which full performance curves and wake maps were measured.}
\label{tab:Re}
\end{table}

A wake map was generated by positioning a Nortek Vectrino+ acoustic Doppler Velocimeter (ADV) at

\subsection{Data Processing}

@@

\subsection{Performance Curves}

@@

\subsection{Wake Characteristics}
